\acknowledgments

First I would like to thank my family for their unconditional support during the past three years. It is their optimistic attitudes as well as patience that helped me walk across all the troubled water among the years.

I would also like to express my deepest gratitude to my advisor Prof. Pan Hui for his support, guidance and encouragement, without which this thesis would not have been possible.

Special thanks to Jiayu Su, it was a great pleasure to collaborate with her in the past year and I learned a lot from the collaboration. Same thanks gives to Dr. Tongfeng Weng for the enjoyable collaboration on random walks. Other than that, I would like to thank Haris Mughees and Hamza Zia, for countless times we happily talked about everything and I was always surprised by their knowledge, passion as well as determination.

Thanks also goes to all the members in Symlab family. I am fortunate to know so many wonderful people and work as college with them. They have helped me a lot in many aspects from daily life to research. Many thanks to Mr. Issac Ma and Mrs. Connie Lau for their administration work.

Last but not least, I would like to thank Prof. Dit-Yan Yeung and Prof. Chi-Keung Tang. It was great fun to take their courses, which guided me to find my interests and thesis topic. I deeply admire the strong sense of responsibility they have on both lecturing as well as supervision of their students. Their research attitudes and hard working will keep motivating me in my future endeavors.

\endacknowledgments
